Detection and Classification of Supernova Gravitational Waves Signals: A Deep Learning Approach

### 2020-04-29 Response_to_PRD_reviewers.txt

* [Fig. 9b] TAP_HLVK and TAP_H+L+VK as a function of distance between
0.5kpc - 200kpc at FAP=0.1%, 0.01%, and 0.001%

Looking at Fig. 7, however, I question if it is possible to achieve
such low FAPs with this pipeline, particularly for the neutrino
mechanism waveforms. It would be useful to remake this figure at
distances for which FAP << 0.3% is possible. If not possible, it may
be beneficial to remove the figure. If not removed, the caption and
text should be updated to note the large FAPs used.

Response: We have tested again the trained CNN with 1.08^6 test samples 
          for each distance so that we can achieved a FAP of 0.1%, 0.01% 
          and 0.001%.

          We appreciate that re-running the simulations at closer
          distances is advised. However, re-running the simulations 
          at closer distances and generating more testing samples to achieve
          the requested FAPs are both computationally expensive.
          We chose to do the latter one as it has the greatest impact on the results 
          and that aligned more strongly with the referees broader comments.

@@

          4. The number of training/test samples in the last paragraph of 
             section III has been updated to be consistent with 
             this change.

          5. We would also like to highlight the fact that the plots
             previously submitted as Fig. 9a and Fig. 9b were actually 
             duplicates of previous Fig. 6a and Fig. 6b by accident. 
             Although this mistake was naturally corrected when we updated
             the results, we would still like to bring this mistake to the
             reviewers' attention.

Overall, the study is a novel and interesting work. It is crucial,
however, to put the authors' pipeline through more rigorous testing
(i.e. at realistic FAPs, perhaps using realistic noise) before stating
its ability to detect GWs from Galactic CCSNe. I would suggest framing
instead the paper as a follow-up pipeline, but take note that the
authors explicitly distinguish their pipeline from that shown in a
similar work by Astone+2018 as designed to take time series directly
from the detectors and find signals, rather than analyzing triggers
found by some external detection pipeline. Given this, it seems
appropriate for appreciable corrections to the text and results to be
requested.

Response: We appreciate this comment and admit that testing/training 
          the CNN using realistic noise would indeed show a more 
          realistic results.
          However, such an extension of the current work would require 
          a whole new set of treatments that we feel is beyond the current scope
          of this work. 
          We have therefore updated our results with more realistic 
          values of FAP and leave tests using realistic noise for future 
          work. In addition, we modified the first paragraph of conclusion
          to include a statement about the use of Gaussian noise.
